%%
%%
%%

\documentclass{resume}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%% NAME SECTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{minipage}{0.55\linewidth}
\name
    {ALICE} {WONDER} % Name {first} {last} 
    {Professional Rabbit Chaser} % Professional Title
\color{black}
\end{minipage}%
%$$$$$$$$$$$$$$$$$$$$$$$$$ CONTACT..SECTION $$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$$%
\vspace{10pt}
\begin{minipage}{0.45\linewidth}
\contact
    {(123) 456-7890} % Phone number
    {alicewonder@madhatter.in} % Email 
    {Cake St, Apt XX, Nowhere, NW 11111} % Address
    {https://www.linkedin.com/in/alice-123-312321-2ad2/} % Linked in Profile
    {Teaparty, underland, OO} % Location
\end{minipage}%
\\
\noindent\makebox[\linewidth]{\rule{590pt}{1.0pt}} \vspace{5pt}
%...................................LEFT BAR..................................................%
\vspace{10pt}
\begin{minipage}{0.60\linewidth}
%%%%%%%%%%%%%%%%%%%%%%%%%%% WORK %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{WORK EXPERIENCE}
 \fontspec[Path=res/fonts/Quicksand/]{Quicksand-Regular}\color{sub}\large
 \subsection{Senior Dreamer, White Queen Army}
\sub{Cheshire Cat} \\
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}\faCalendar \vspace{1pt} 
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}Aug 2017 - May 2019
\begin{itemize}
\fontspec[Path=res/fonts/Quicksand/]{Quicksand-Medium}\color{sub}\fontsize{12pt}{10pt}
    \item \xbody{y began at Folly Bridge near Oxford and ended five miles away in the village of Godstow. During the trip Charles Dodgson told the girls a story that featured a bored little girl named Alice who goes looking for an adventure.}
    \item \xbody{ told the girls a story that featured a bored little girl named Alice who goes looking for an adventure. The girls loved it, and Alice Liddell asked Dodgson to write it down for her. He began writing.}
    \item \xbody{ut before Alice received her copy, Dodgson was already preparing it for publication and expanding the 15,500-word original to 27,500 words}
\end{itemize}
 \subsection{Big Girl, Red Queen Clique}
\sub{Lobster Quadrille} \\
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}\faCalendar \vspace{1pt} 
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}Aug 2017 - May 2019
\begin{itemize}
\fontspec[Path=res/fonts/Quicksand/]{Quicksand-Medium}\color{sub}\fontsize{12pt}{10pt}
    \item \xbody{ears, is feeling bored and drowsy while sitting on the riverbank with her elder sister.}
    \item \xbody{ears, is feeling bored and drowsy while sitting on the riverbank with her elder sister. Sheos. She finds a small key to a door too small for her to fit through, but through it she sees an attractive garden. She then discovers as}
    \item \xbody{The girls loved it, and Alice Liddell asked Dodgson to write it down for her. He began writing}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%.Voluteer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{VOLUNTEER EXPERIENCE}
 \fontspec[Path=res/fonts/Quicksand/]{Quicksand-Regular}\color{sub}\large
 \subsection{Senior Manager, Design Committee}
\sub{Ragam 2016} \\
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}\faCalendar \vspace{1pt} 
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}Aug 2017 - May 2019
%%%%%%%%%%%%%%%%%%%%%%% OTHER THINGS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{OTHER THINGS} \vspace{3pt}
\begin{itemize}
\fontspec[Path=res/fonts/Quicksand/]{Quicksand-Medium}\color{sub}\fontsize{12pt}{10pt}
    \item PUBLICATIONS feeling bored and drowsy while sitting on the riverbank with her elder sister. Sheos. She finds a small key to a door too small for her to fit through, but through it she sees an attractive garden. She then discovers as ng bored and drowsy while sitting on theriverbank with her 
    \item PERSONAL PROJECTS ng bored and drowsy while sitting on theriverbank with her elder sister elder sister and brother cat hat mat boat xx blah blah
    \item AWARDS ng bored and drowsy while sitting on theriverbank with her elder sisterelder sister and brother cat hat mat boat xx blah blah
    \item COURSEWORK, etc feeling bored and drowsy while sitting on the riverbank with her elder sister. Sheos. She finds a small key to a door too small for her to fit through, but through it she sees an attractive garden. She then discovers as
\end{itemize}
\end{minipage}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RIGHT SIDE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hspace{15pt}
\begin{minipage}{0.35\linewidth}
\color{black}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EDUCATION}
\subsection{Masters. in Computer Science}
\fontspec[Path=res/fonts/Quicksand/]{Quicksand-SemiBold}\color{body}\fontsize{10pt}{10pt} University Of Twins At Twins \\ \vspace{3pt}
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}\faCalendar \vspace{1pt} Aug 2017 - May 2019 \\ \vspace{3pt}
\fontspec[Path=res/fonts/Quicksand/]{Quicksand-SemiBold}\color{sub}\fontsize{10pt}{10pt} GPA : inf.83 \vspace{3pt}
\subsection{B.Tech in Computer Science}
\fontspec[Path=res/fonts/Quicksand/]{Quicksand-SemiBold}\color{body}\fontsize{10pt}{10pt} University Of Twins At Twins \\ \vspace{3pt}
\fontspec[Path=res/fonts/Opensans/]{OpenSans-RegularItalic}\color{sub}\fontsize{10pt}{10pt}\faCalendar \vspace{1pt} Jul 2012 - May 2016 \vspace{3pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SKILLs %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SKILLS}
\subsection{Programming Languages}
\vspace{.05cm}
\skills{Python}{.8}
\skills{C++}{.75}
\skills{Rust}{.65}
\skills{Scala}{.5}
\skills{Java}{.45}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ADDITIONAL SKILSS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Familiar Languages}
\psframebox{C\#}
\psframebox{Lua}
\psframebox{HTML}
\psframebox{CSS}
\psframebox{MATLAB}
\psframebox{Shell}
\psframebox{\LaTeX}
\subsection{Other Skills}
\psframebox{Linux}
\psframebox{PyTorch}
\psframebox{TensorFlow}
\psframebox{OpenGL}
\psframebox{GLSL}
\psframebox{OpenCV}
\psframebox{GIT}
\psframebox{Unity Engine}
\psframebox{Junit}
\psframebox{Numpy}
\psframebox{Scikit-Learn}\\
\vspace{3pt}\hdashrule{\linewidth}{1pt}{3pt}
\psframebox{Team player}\psframebox{Problem Solver}\psframebox{Self-Motivated}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWRADS And  CERFICATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CERTIFICATIONS}
\begin{itemize}
    \renewcommand{\labelitemi}{\large\faSunO}
    \item\xboldbody{Coursera :- Improving netherland copying other show and somekind of Optimization is required maybe}
    \item\xboldbody{DANcEing something app xx yyy}
    \item\xboldbody{Coursera :- eHatter speicaliztion with bounus pointsh}
    \item\xboldbody{Coursera :- flower painting basic in wonderland}
    \item\xboldbody{Coursera :- Evil queen something white good probably i dont know}
\end{itemize}
\end{minipage}
%.....................................BOTTOM SECTION..............................................%
\color{black} 
\end{document}